Multisensor Architecture for an Intersection Management System

### 2018-06-18 ch1-introduction.tex
Minor modifications. Apendix removed

Traditionally, transport systems vision has been constrainted to the set of elements belonging to infrastructure and the vehicles using it. As population increases and cities growth, the number of vehicles going through world roads also increases, but the growth rate of road network is lower. This situation leads to low quality in transportation; congestion and collisions affect movility in all cities in the world and the costs of eficient and long-lasting solutions are high.

>>>>

Traditionally, the vision of transport systems has been constrainted to the set of elements belonging to infrastructure and the vehicles using it. As population increases and cities growth, the number of vehicles going through world roads also increases, but the growth rate of road network is lower. This situation leads to low quality in transportation; congestion and collisions affect movility in all cities in the world and develop of efficient and long-lasting solutions carries high costs.
